\section{Question 2}  
\textbf{Outline your investment objectives, constraints and strategies and discuss the relative importance of risk and return in your investment decision making.}

\paragraph*{Objectives and Constraints}
The portfolio's main objective is long-term growth and capital appreciation, which is defined as a rise in an investment's market price. Given our young age, the limited initial capital available is the main constrain. Because of our risk-tolerance profile, we do not explicitly specify a loss limit. As a general rule, if a holding asset presents a one-year loss of its value greater that 20\%, then it should be considered for exclusion from the portfolio.

\paragraph*{Investment Strategy}
The main investment vehicles are stocks highlighted for their growth potential. We mainly focus on the technology sector or sectors that directly benefit from advancements in technology and innovations. A small amount is also allocated to corporate bond funds of medium credit quality (A and/or BBB) and to precious metals, for diversification purposes.

The final selected assets from each category are presented and analysed below:

\subsection{Stocks}
A total of six stocks are selected for the portfolio:

\paragraph*{Broadcom Inc. (Large/High-Dividend)}
Broadcom Inc. is a global leader in designing and developing semiconductor and software infrastructure solutions. Broadcom's product portfolio serves data centres, networking \& telecom hardware and high-end smartphone components. In January 2020, Broadcom announced a \$15 billion deal with Apple to supply upcoming iPhone products with wireless chips. With new 5G technology well under-way towards global scale deployment, Broadcom will gain the opportunity to expand its business and develop 5G compatible components. Even though currently is categorised as a "value" type stock, we believe it has a good growth potential in the future.

\paragraph*{ServiceNow Inc. (Large/Growth)}
ServiceNow Inc. is a provider of cloud-based software solutions to structure, manage and automate business processes for global enterprises. The company delivers services based on a Software as a Service (SaaS) model, and its main focus is IT service management. However, more recently it expanded the available workflow solutions to other departments, such as Customer Support, Human Resources and Security Operations. It targets a wide range of industries including financial services, healthcare, government and education.

\paragraph*{Tesla Inc. (Large/Growth)}
Tesla Inc. is a leading auto manufacturer company for next-generation electric vehicles, while also a designer and operator of sustainable energy systems. Tesla is a global leader in electric mobility and will benefit from the increasing global social responsibility regarding fuel emissions. At the moment Tesla operates 3 Gigafactories worldwide, while also constructing a forth one in Berlin. It is expected to begin operations in July 2021 and will enable Tesla to establish a stronger presence in Europe. Global vehicle deliveries were 367,656 units in 2019 and we expect this figure to grow in the upcoming years, as more advancements in battery technology will allow electric vehicles to increase their autonomy and become a wider commercial product.  

\paragraph*{Amazon Inc. (Large/Growth)}
Amazon Inc. is one of the biggest online retailers, recently reaching the \$1 trillion market cap for the second time in the last 3 years. Its core business are online product and digital media sales, however we believe a higher potential lies in its Amazon Web Services Department. AWS offers solutions for machine learning, big data, IoT, cloud-computing and storage application. All of these technological fields are expected to greatly advance in the upcoming years and therefore further boosting the company growth.

\paragraph*{Iridium Communications Inc. (Small/Growth)}
Iridium Communications Inc. is a leader in providing global voice and data services with satellite communications. It operates and maintains a vast network with over 70 satellites in orbit and related ground infrastructure, achieving true global coverage. In 2018 a partnership was announced with Amazon Web Services, aiming to develop a satellite network for future IoT applications. The company's commercial end user base includes business and organisations of various sectors, including maritime, aviation, government \& military, emergency services, oil \& gas, mining and transportation.

\paragraph*{Broadridge Financial Solutions Inc. (Mid/Aggressive Growth)}
Broadridge Financial Solutions Inc. is a provider of communications and technology-driven solutions to investors, banks, brokerage offices, mutual funds and corporate issuers. The company delivers a range of solutions, including communication platforms, securities processing and data analytics that aid its clients in improving their quality of customer services, along the whole life cycle of an investment.

\subsection{Bonds}
A total of two corporate bond mutual funds are selected for the portfolio:

\paragraph*{Payden Corporate Bond Mutual Fund}
The fund invests in a variety of debt instruments and income generation securities. It invests at least 85\% of its assets in corporate bonds of mainly A and BBB credit rating. It may also use derivative products, such as CDS in order to gain exposure to the corporate debt market.

\paragraph*{Western Asset Corporate Bond Mutual Fund}
The fund invests at least 80\% of its assets in corporate debt securities, while 10\% of the assets might be non-U.S dollar nominated fixed income securities of foreign issuers. The majority of holding assets are of A and BBB credit rating.

\subsection{Commodities}
A total of two precious metals are selected as commodities:

\paragraph*{Gold}
After reaching historical lows in 2015, gold has since then seen a significant rise in value. The precious metal is traditionally considered a safe investment during rough economic times and a hedge against inflation. Recently investors are turning to gold as safe houses instead of government bonds, as the latter had negative inflation-adjusted returns in 2019. Due to this fact investors have shifted their focus to gold, because even though is does not generate any return, it also does not have any holding costs and thus is more favourable for the time being.

\paragraph*{Palladium}
Palladium is now more expensive than the four major precious metals, as its value has almost doubled over the last year. Palladium's main commercial use is in catalytic converters of car's exhaust systems, that help turn toxic gas emissions into less harmful ones. This impressive rise in price can be solely explained by the fact that demand outstrips supply. Palladium is a secondary product from mining operations of other metals, such as platinum or nickel and thus miners have less control over the extracted quantities in response to prices rising. Palladium production is projected to fall short of demand for the 8$^{th}$ straight year and therefore the metal is expected to maintain its current market value.

\subsection{Overview}
The portfolio aims in capital appreciation and focuses on assets, such as stocks, that traditionally are more volatile and thus bear more risk. However they may also generate higher returns compared to less risky assets, hence their selection as the main investment instrument of the present portfolio.


