\section{Question 3}  
\textbf{Provide a preliminary discussion of the effects of the short investment horizon in your decision(s) and diversification strategy}

The investor's time horizon plays a crucial role in choosing the instruments of a portfolio. As stated previously, our main objective is long-term capital appreciation and the primary selected asset are stocks. Stocks are widely considered as risky assets, but they also tend to generate higher returns over long periods of time compared to other less risky assets, such as bonds.

If an investor wants to make an investment of short-term horizon, then stocks probably should not be the preferred asset, as their prices usually have substantial fluctuations over short periods of time, affected by temporary financial, social as well as geopolitical news and events. Therefore the desired return might not be realised, leaving the investor short on his target. Bonds should be a more favourable choice in this occasion, as they are less risky (in terms of variability) and provide a relatively steady generation of income over the short period.

However, this does not mean that a long-term portfolio should not include bonds. One of their important roles is that they reduce overall volatility, as their returns present very low or negative correlation values with stock returns. Additionally, they offer some protection against any emergency short-term capital or liquidity needs that may arise, in the form of regular interest payments.

In conclusion, our diversification strategy can be summarized as follows:
\begin{itemize}
	\item Even though we focused on growth style stocks, our choices included companies of different market capitalizations (Large, Mid, Small) and industry sectors (i.e Semiconductors, Communication Services, Online Retail and Cloud Services).
	\item Two corporate bond mutual funds were included in the portfolio, for the reasons analysed above.
	\item Two commodities were also included, as a hedge against inflation and for risk reduction, since they exhibit low or negative correlation values with stock assets.
\end{itemize}