\section{Question 8}
\label{events}
The time frame of this project happened to coincide with the outbreak of Covid-19 pandemic. To counter the pandemic, approximately 3 billion people are currently living under quarantine in over 70 countries, which has caused major economic and social disturbances. In the midst of this crisis, we will try and identify events that influenced the value of our portfolio's assets, for the period 1/14/2020 - 4/20/2020:

\paragraph*{Broadcom Inc. (Down -16.2 \%)} Due to the coronavirus originating in China, the most immediate impact of the pandemic has been a disruption to supply chains, as plants and factories that are used by technology companies were forced to shutdown. For example, the primary manufacturer of iPhone components, Foxconn, ceased most of its production. This has led to reduced forecasts in iPhone shipments, which in turn has also affected the business of Broadcom, who is a major supplier for Apple's wireless chips.

\paragraph*{ServiceNow Inc. (Down -3.2 \%)} Being a cloud-based software solutions company, ServiceNow has maintained business continuity and may also benefit in the near future, as the workflow automation processes that it provides might be crucial for businesses to adapt to new work-from-home operational status.

\paragraph*{Tesla Inc. (Up +38.53 \%)} Despite of major auto-manufacturers reporting big declines in sales for the quarter, Tesla managed to sustain sales and production, in spite of the shut down of a factory in California. The record-level productivity that was achieved at a Gigafactory in Shanghai (which only closed for two weeks in early February) is credited for this success. A total of 88,400 vehicles were delivered, far exceeding the expectations.

\paragraph*{Amazon Inc. (Up +28.8 \%)} Online retail trade and e-commerce have seen a steep rise in sales in March 2020, as high as 74\% in the UK compared to March 2019. Being a leader in online retail, Amazon has experienced increased demand during the period of imposed quarantine conditions around the world.

\paragraph*{Iridium Communications Inc. (Down -11.7 \%)} According to mid-March statements from the CEO, Iridium does not expect a major impact to business from the coronavirus outbreak. The company's inventory of equipment is solid in numbers, since currently no satellites are on the assembly line and no launches are scheduled. There might be a revenue loss from services provided to airline corporations, as they have been one of the hardest hits and are forced to cut down costs, but Iridium still provides its communication services to a significant amount of other sectors and industries.

\paragraph*{Broadridge Financial Solutions Inc. (Down -16.4 \%)} Broadridge offers financial services to various businesses and institutions. Certain aspects of their services have seen a decline in demand, such as equity underwriting procedures, since many companies delay their IPO's until the market stabilizes. On top of that, a class-action law suit has been filed against Broadridge from the 200 employees that work on a leased printing warehouse, claiming that they have not been compensated for non-standard work hours and overtime during the virus outbreak period.

\paragraph*{Corporate Bond Mutual Funds (Down approx. -2.0 \%)} The selected corporate bond mutual funds had holdings with medium credit quality and have seen a small decline in value, as investors seek for higher investment-grade debt issuers.

\paragraph*{Commodities} Palladium has maintained its high value (down only -0.7 \%) and seems unaffected by the pandemic, whereas gold has increased by 11 \% in value, since it is considered a safe-house for investors during rough economic times.

















